Supplementary Materials

### 2018-11-29 Manuscript/sup_mat.tex
paper edits
streamlining methods and results

>>>>

Stimuli consisted of arrays of black oriented line segments against a grey background. Each line segment had a length of $\approx$$1.6^{\circ}$ of visual angle irrespective of screen resolution. The target was oriented $45^{\circ}$ clockwise, while the distractor items had a random orientation with a mean of $45^{\circ}$ anti-clockwise. The variance was low ($18^{\circ}$) on one half of the display to create a homogeneous texture, and high ($95^{\circ}$) on the other side to create a heterogeneous texture. This means that when the target is present on the homogeneous half, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect. This was verified in a pilot experiment reported in \cite{nowakowska2017}.  There were 160 trials in total and homo- and heterogeneous sides of the display were randomly varied from trial to trial. The position of the dominant eye was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada).

This paradigm was carried out twice, once in each testing session, to give us an estimate of how consistent participants are in their search strategy over time.
